Toward Intelligent Refactoring Recommendations

### 2016-08-22 Manuscript.tex
Updates from ShareLaTeX

\title{How to Discourage Useless Refactorings}

@@

\begin{abstract} 
{\bf Context: } 
Developers use code bad smells to guide their refactoring (reorganizing their code).
Yet developers, text books, and tools disagree on which bad smells are important.
%Many bad smell detectors recommend refactoring when static code measure
%cross some threshold boundary. 
%%However, it is unclear at what threshold values smell-related metrics
%should trigger code improvement or preventative maintenance.

\noindent 
{\bf Objective: } We seek to introduce a tool that can recognize  useless refactorings.

\noindent
{\bf Method: } We introduce XTREE, a tool which, given a historical log of defects seen previously in the code, generates
a set of useful code changes.
Any bad smell that requires changes outside of that set can be deprioritized 
(since there is no
historical evidence that the bad smell causes any problems).

@@

\noindent
{\bf Conclusion: }
Before undertaking a refactoring based on a bad smell report,
use a tool like XTREE to check and ignore any refactoring   that  are useless; i.e. which lacks evidence
  in the historical record  that it is useful to make that change.
  Note that this use case applies to both manual refactorings proposed by developers
as well as refactoring  conducted by automatic methods.
This recommendation assumes that there is an historical record.
If none exists, then the results of this paper could be use used as a guide (see our
Table~8).

@@

According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these \underline{refactoring} transformations is quite significant. By doing them in small steps you reduce the risk 
of introducing errors''.
\end{quote}
Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.
Hence it is important to understand the value of
this popular topic.  
Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

In our experience, programmers can use the SE literature to justify extensive, perhaps even excessive, refactoring efforts.
For example, this paper began when a Washington-based software company shared
one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. This management team wanted some way to check if all that activity was useful.

Note that these managers are {\em not} asking for better
automatic refactoring
tool support. Their human programmers are refactoring
code all the time, perhaps too much so.
Hence, their management goal is: 
\bi
\item
{\em Not} to optimize {\em necessary} refactorings;
\item
But rather to discourage {\em unnecessary} refactorings.
\ei
For those managers, we offer the  following heuristic:
\bi
\item If there is no evidence in the historical record that changing ``X'' is useful;
\item Then discourage developers from doing ``X''.
\ei
This paper describes one way to operationalize this heuristic, in the context
of assessing bad smells. We use data mining to generate two oracles: a {\em primary
change oracle} and a {\em secondary verification oracle}.
By combining these two oracles,
 we can generate and validate useful
changes to code modules.

In this paper, we use 
the XTREE cluster delta algorithm as the {\em primary change  oracle}.
XTREE 
explores the historical record of a project to find clusters of projects.
It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects$C_1$ (so $\Delta$
is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an entropy measure.

As to 
the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
sensible changes. For this purpose we use Random Forest\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
 In our framework,  learning
the secondary oracle is   a {\em separate} task from that of learning the primary
oracle. This  ensures that the verification oracle offers an independent
opinion on the value of the proposed changes.

When these oracles were applied to defect data from
open source object-oriented software systems, we discovered a {\em conjunctive fallacy}
in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
A common heuristic is to recommend refactoring of ``bad'' code
to make it ``better''   as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
\begin{equation}\label{eq:df}
\scriptstyle
\begin{array}{rl}
\mathit{bad} & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee    ... \\
\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) \bigwedge \left(a_2 \le t_2\right)  \bigwedge  ...
\end{array}
\end{equation}
We say that the above definition of ``better'' is a conjunctive fallacy
since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
to remove the ``bad'' smells. This is wrong.  
There exists an intricate set of associations between static code measures
such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
It is easy to see why this is so.
A requirement for  refactoring is that the new code supports the same functionality
as before. If we pull code out of a function (since that function has grown too
large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
recommendation is that if we decrease a module's lines of code  then in the refactored
code, the functionality is achieved via a communication between several different parts
of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
that module's coupling metrics.

@@

This paper  claims that (a)~XTREES is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very 
small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
static code measures). 
In support of these claims, 
the rest of this paper is structured as follows. First, we offer some background on bad smells. After that,
  in Section~3, 
  different methods are presented for determining when code does/does not have bad smell. One of those methods
  will be XTREE while the others will come from other researchers. Next,    Section~4
  defines an assessment method that checks which of these methods is most useful. The results from that assessment 
  are presented in Section~5. Those results will answer five research questions.

 {\bf  RQ1: Effectiveness}: According to the verification oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
  code modules should be changed? To answer this question, we used data from five OO Java projects
  (Ivy, Lucene, Ant, Poi, Jedit). It was found that:
  \begin{lesson}
 XTREE is the best oracle on how to change code modules (in order to reduce defects).
  \end{lesson}

 {\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. affect fewest attributes) then those changes
will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
code attributes?
\begin{lesson}
Of all the code change oracles studied here, XTREE recommend  far fewest changes to static code measures.
\end{lesson}

@@

 {\bf RQ4: Stability}: Across different projects, how variable are the changes recommended by our best change oracle?
\begin{lesson}
The direction of change recommended  XTREE is  very stable across repeated runs of the program 
\end{lesson}

@@

\subsubsection{ Shatnawi}
Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
thresholds which, following Shatnawi's guidance, we set to
$p_0=p_1=0.05$.

VARL encodes the defect count
for each class as 0 (no defects known in class) or 1 (defects known in class).
Univariate binary logistic regression is applied to learn three coefficients:  
 $\alpha$ is the intercept constant;
    $\beta$ is the coefficient for maximizing log-likelihood;
  and $p_0$  
    measures   how well this   model predicts for   defects.
Any code metric with $p_0>0.05$ is  ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
an equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}

@@

For consistency
with Shatnawi, we explore the correlation between
the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).

\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction fallacy}  discussed in the introduction.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what minimal
metrics need to be changed at the same time (or whether or not those
changes lead to minimization or maximization of static code measures).

@@

Cluster deltas are a general method
for learning {\em conjunctions} of changes
that need to be applied at the same time. 
This approach works as follows:
\begin{itemize}
    \item Cluster the data. 
    \item Find
neighboring clusters $C_+,C_-$ where $C_+$ has more examples of defective
modules than $C_-$;
\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$}, i.e.
{\em towards} the cluster with lower defects;
\item $\Delta$ are changes needed in defective modules of $C_+$ to
      make them more like the less-defective modules of $C_-$
\end{itemize}
Note that $\Delta$ is a conjunction of  recommendations.
Since it is computed
from neighboring clusters, the examples contain similar distributions and $\Delta$ respects the naturally occurring constraints in the data. For example,
given a bad smell pertaining to large methods,   $\Delta$   will not  suggest lowering lines of code
without also increasing a coupling measure. 
Cluster deltas are used in CD~\cite{me12c} and XTREE.

@@

  XTREE  is a cluster delta algorithm
  that avoids the problem of verbose $\Delta$s.
  It is our recommended {\em primary change oracle} that makes recommendations 
  of what changes should be made to code modules.
  Instead of reasoning over cluster centroids,
  XTREE utilizes a decision tree learning approach
  to find the fewest differences between clusters of examples.

 XTREE uses an iterative dichotomizer that
first converts the values for each code
metrics into a small number of ranges.
Consider a code metric is split into $r$ ranges and each range is of
  size
    $n_r$ is
  associated with a set of defect counts $x$ with standard deviation
  $\sigma_r$.
  The best split for that range is
  the one that minimizes the expected value of the
  defect variance, after the split; i.e.
  $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$).
  This discretizer then recurses on each part of the split
  to find other splits.

  When discretization finishes, each code metric $M$ has a 
  final expected value $M_v$ for the defect standard deviation 
  across all the discretized ranges of that metric.
  Iterative dichomization sorts the metrics by $M_c$
  to find the best ``splitter'' for the data
  (the code metric with smallest $M_v$). The data
  is then split on the ranges of the splitter and
  iterative dichomization recurses on each range.  In this way,
  each split is the root of a sub-tree.

@@

Next, for each test code module, 
	  find $C_+$ as follows take each test , run it down to a leaf in the decision tree.  
After that,	  find $C_-$ as follows:
		\begin{itemize}
		\item Starting at the  $C_+$ leaf, ascend   $lvl\in \{0,1,2...\}$ tree levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
		\item Find the {\em better} siblings; i.e. those 50\% (or less)
		fewer defects than $C_+$.
		   If none found, then repeat for $lvl += 1$. Also,
		    return nil  if the new $lvl$ is above the root. 
		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Now find $\Delta = C_+ - C_-$  by reflecting
	 on the set difference between  conditions in the decision tree branch to $C_-$ and $C_+$. To find that delta,
	 for discrete attributes, the delta is the value from {\em desired};
	    for numerics  expressed as ranges, the delta is a random number selected from the low and high boundaries of the that range.

@@

{\bf RQ1: Effectiveness: } which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? 
To   answer to this question, we will assume that developers
refactor their code until the bad smell thresholds is not violated.
This refactoring will start with some {\em initial} code
base that is changed to a {\em new} code base. 
For example, if the bad smell is \mbox{{\em loc $>100$}} and a 
code module has 500 lines of code, we reason
optimistically that we can change that code metric
to 100.  
Using the secondary verification oracle,  we then predict the
number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
The best bad smell threshold method is the one that maximizes
\begin{equation}\label{eq:diff}
\mathit{improvement} = 100* \left(1 - \frac{ d_- }{ d_+}\right)
\end{equation}

@@

{\bf RQ4: Stability:} Across different projects, how variable are the changes recommended by XTREE?   To answer this
question, we conduct a large scale ``what if'' study that reports all the possible recommendations XTREE might make.
We then count often attributes are {\em not} found in the recommendations arising from this ``what if'' study.

{\bf RQ5: Conjunctive Fallacy:} Is  it  always  useful  to  aplly \eq{df}; i.e.   make  code  better  by  reducing  the  values  of multiple code attributes? To answer this question, we will look at the {\em direction of change} seen in the {\bf RQ4} study; i.e.
how often does XTREE recommend decreasing or increasing a static code attribute.

@@

\subsection{Statistics}

@@

\fig{counts} shows the frequency with which the methods
recommend changes to specific code methods.
Note that XTREE proposes thresholds to
few code metrics compared to the other approaches.

@@

{\em  How effective is XTREE at offering   “stopping points” (i.e. clear guidance on what not to do)?}

@@

\subsection{RQ5: Stability}

@@

To explore this point further, we conducted the following ``what-if'' study. Once XTREE builds its trees with its leaf clusters then:
\be
\item For all clusters $C_0$, $C_1$ where the percent of defects in $C_0$ is greater than $C_1$...
\item For all attribute measures that are have a statistically significantly different distribution  between $C_0$ and $C_1$...
\item Report the direction of the change.
\ee
Note that the changes found in this way are somewhat more general than the above results
since they were  limited
to comments on the test set given to the program. The above three points comments on the direction of {\em all possible changes}
that XTREE could ever report

>>>>

% \title{How to Discourage Useless Refactorings}
\title{Toward Intelligent Refactoring Recommendations}

@@

\begin{abstract} 
{\bf Context: } 
Developers use bad code smells to guide refactoring.
Yet developers, text books, tools, and researchers disagree on which bad smells are important.
%Many bad smell detectors recommend refactoring when static code measure
%cross some threshold boundary. 
%%However, it is unclear at what threshold values smell-related metrics
%should trigger code improvement or preventative maintenance.

\noindent 
{\bf Objective:} To evaluate the likelihood that a refactoring to address bad code smells will yield improvement in the defect-proneness of the code.

\noindent
{\bf Method: } We introduce XTREE, a tool that analyzes a historical log of defects seen previously in the code and generates a set of useful\footnote{Need to define useful in precise terms} code changes.
Any bad smell that requires changes outside of that set can be deprioritized (since there is no historical evidence that the bad smell causes any problems).

@@

\noindent
{\bf Conclusion: }
Before undertaking a refactoring based on a bad smell report,
use a tool like XTREE to check and ignore any refactorings   that  are useless; i.e. which lacks evidence
  in the historical record  that it is useful to make that change.
  Note that this use case applies to both manual refactorings proposed by developers
as well as refactoring  conducted by automatic methods.
This recommendation assumes that there is an historical record.
If none exists, then the results of this paper could be use used as a guide (see our
Table~8).

@@

According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these \underline{refactoring} transformations is quite significant. By doing them in small steps you reduce the risk 
of introducing errors''.
\end{quote}

Bad smells are a widely used technique for evaluating code. While the original bad small concept was largely subjective [REF], researchers including Marinescu [REF] and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics. Consequently, code smells are captured by popular static analysis tools such as PMD [REF], CheckStyle [REF], FindBugs [REF], and SonarQube [REF], although not always explicitly labeled as such.

Refactoring bad smells from code is generally accepted as a recommended practice, but refactoring by definition does not change the external functionality of the system and thus may have no perceived value. For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. 
%This management team wanted some way to check if all that activity was useful. 
Kim et al.\cite{kim2012field} surveyed developers at Microsoft and found that refactoring incurs significant cost and risks. A Google search on the terms ``refactoring cost'' yields numerous threads on StackOverlfow from developers asking how to justify refactoring and when the costs of refactoring outweight its benefits.

% As of  early 2016, the ACM Digital Library reports 
% the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on \texttt{``bad smell'' programming 
% where proceedings=ICSE} in the ACM Digital Library finds 1,748 papers since 2006.
% Hence it is important to understand the value of
% this popular topic.  
% Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
%  irrelevant or misleading
% for some particular project.

% In our experience, programmers can use the SE literature to justify extensive, perhaps even excessive, refactoring efforts.
% For example, this paper began when a Washington-based software company shared
% one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code. This management team wanted some way to check if all that activity was useful.

% In addition to tools that capture bad smells such as FindBugs and SonarQube, a multitude of tools have been proposed to support refactoring (e.g., \cite{ge2014manual,lee2013drag,foster2012witchdoctor,ge2012reconciling}). Note that these managers are {\em not} asking for better
% automatic refactoring
% tool support. 
% Their human programmers are refactoring
% code all the time, perhaps too much so.
% Hence, the management goal
The challenge is to encourage refactorings that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid refactorings with no demonstrable benefit and thus waste effort.

This paper describes one approach to evaluate whether refactorings that change the structure of code are likely to have a perceivable benefit by evaluating:
\bi
\item If there is no evidence in the historical record that changing ``X'' is useful;
\item Then discourage developers from doing ``X''.
\ei
We use data mining to generate two oracles: a {\em primary
change oracle} and a {\em secondary verification oracle}.
By combining these two oracles,
 we can generate and validate useful
changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube [REF] and Klocwerk [REF].

In this paper, we use 
the XTREE cluster delta algorithm as the {\em primary change  oracle}.
XTREE 
explores the historical record of a project to find clusters of module.
It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects $C_1$ (so $\Delta$
is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an entropy measure.

As to 
the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
sensible changes. For this purpose we use Random Forest~\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
 In our framework,  learning
the secondary oracle is   a {\em separate} task from that of learning the primary
oracle. This  ensures that the verification oracle offers an independent
opinion on the value of the proposed changes.

When these oracles were applied to defect data from
open source object-oriented software systems, we discovered a {\em conjunctive fallacy}
in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
A common heuristic is to recommend refactoring of ``bad'' code
to make it ``better'' as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
\begin{equation}\label{eq:df}
\scriptstyle
\begin{array}{rl}
\mathit{bad} & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee    ... \\
\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) \bigwedge \left(a_2 \le t_2\right)  \bigwedge  ...
\end{array}
\end{equation}
We say that the above definition of ``better'' is a conjunctive fallacy
since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
to remove the ``bad'' smells. In reality, there exists an intricate set of associations between static code measures
such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
It is easy to see why this is so.
A requirement for  refactoring is that the new code supports the same functionality
as before. If we pull code out of a function (since that function has grown too
large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
recommendation is that if we decrease a module's lines of code  then in the refactored
code, the functionality is achieved via a communication between several different parts
of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
that module's coupling metrics.

@@

This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very 
small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
static code measures). 
In support of these claims, 
the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
  different methods are presented for determining when code does/does not have bad smell. One of those methods
  will be XTREE while the others will come from other researchers. Section~4
  defines an assessment method that checks which of these methods is most useful. The results from that assessment 
  are presented in Section~5. Those results will answer five research questions.

 {\bf  RQ1: Effectiveness}\footnote{test}: According to the verification oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
  code modules should be changed? To answer this question, we used data from five OO Java projects
  (Ivy, Lucene, Ant, Poi, Jedit). It was found that:
  \begin{lesson}
 XTREE is the most accurate oracle on how to change code modules in order to reduce defects.
  \end{lesson}

 {\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. affect fewest attributes) then those changes
will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
code attributes?
\begin{lesson}
Of all the code change oracles studied here, XTREE recommends the fewest number of changes to static code measures.
\end{lesson}

@@

 {\bf RQ4: Stability}: Across different projects, how variable are the changes recommended by our best change oracle?
\begin{lesson}
The direction of change recommended by XTREE is  very stable across repeated runs of the program 
\end{lesson}

@@

\subsubsection{ Shatnawi}
Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
thresholds which, following Shatnawi's guidance, we set to
$p_0=p_1=0.05$.\footnote{There is no p0 in the equation.}

VARL encodes the defect count
for each class as 0 (no defects known in class) or 1 (defects known in class).
Univariate binary logistic regression is applied to learn three coefficients:  
 $\alpha$ is the intercept constant;
    $\beta$ is the coefficient for maximizing log-likelihood;
  and $p_0$\footnote{There is no p0 in the equation.}  
    measures   how well this   model predicts for   defects.
Any code metric with $p_0>0.05$ is  ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
an equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}

@@

For consistency
with Shatnawi, we explore the correlation between
the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).\footnote{Okay, why focus on Shatnawi and not the others? this statement seems out of place.}

\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction fallacy}\footnote{It was conjunctive fallacy in the introduction -- which is right?}  discussed in the introduction.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what minimal
metrics need to be changed at the same time (or whether or not those
changes lead to minimization or maximization of static code measures).

@@

Cluster deltas are a general method
for learning {\em conjunctions} of changes
that need to be applied at the same time. 
This approach works as follows:
\begin{itemize}
    \item Cluster the data. 
    \item Find
neighboring clusters $C_+,C_-$ where $C_+$ has more examples of defective
modules than $C_-$;
\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$}\footnote{Isn't this backward? Doesn't $C_- - C_+$ give you the changes to be made to $C_+$, e.g. $C_+$ = 1000LOC, $C_-$ = 100 LOC, $C_- - C_+$ = -900 LOC which is the transformation you want to apply to $C_+$}, i.e.
{\em towards} the cluster with lower defects;
\item $\Delta$ are changes needed in defective modules of $C_+$ to
      make them more like the less-defective modules of $C_-$
\end{itemize}
Note that $\Delta$ is a conjunction of  recommendations.
Since it is computed
from neighboring clusters, the examples contain similar distributions and $\Delta$ respects the naturally occurring constraints in the data. For example,
given a bad smell pertaining to large methods,   $\Delta$   will not  suggest lowering lines of code
without also increasing a coupling measure. 
Cluster deltas are used in CD~\cite{me12c} and XTREE.

@@

  XTREE  is a cluster delta algorithm
  that avoids the problem of verbose $\Delta$s.
  XTREE is our {\em primary change oracle} that makes recommendations 
  of what changes should be made to code modules.
  Instead of reasoning over cluster centroids,
  XTREE utilizes a decision tree learning approach
  to find the fewest differences between clusters of examples.

 XTREE uses an iterative dichotomizer that
first converts the values for each code
metric into a small number of ranges.
Consider a code metric is split into $r$ ranges and each range is of
  size
    $n_r$\footnote{How do you select $r$ and/or $n_r$?} is
  associated with a set of defect counts $x$ with standard deviation
  $\sigma_r$.
  The best split for that range is
  the one that minimizes the expected value of the
  defect variance, after the split; i.e.
  $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$).
  This discretizer then recurses on each part of the split
  to find other splits.

  When discretization finishes, each code metric $M$ has a 
  final expected value $M_v$ for the defect standard deviation 
  across all the discretized ranges of that metric.
  Iterative dichomization sorts the metrics by $M_v$
  to find the best ``splitter'' for the data
  (the code metric with smallest $M_v$). The data
  is then split on the ranges of the splitter and
  iterative dichotimization recurses on each range\footnote{I get lost here. You found the ranges to split from the smallest $M_v$ and you split the data on that. But what is the ``iterative dichotimization that recurses on each range'' at this point?}  In this way,
  each split is the root of a sub-tree.

@@

Next, for each test code module, 
	  find $C_+$ as follows take each test , run it down to a leaf in the decision tree.  
After that,	  find $C_-$ as follows:
		\begin{itemize}
		\item Starting at the  $C_+$ leaf, ascend   $lvl\in \{0,1,2...\}$ tree levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
		\item Find the {\em better} siblings; i.e. those 50\% (or less)
		fewer defects than $C_+$.\footnote{This example is for number of defects. What is your criteria for defect-proneness classification as in the Figure?}\footnote{Does XTREE stop as soon as it finds a better sibling? If it finds better siblings at level X, how do you know there are not BETTER better siblings at level X+1? It SEEMS like your dichotimization is optimized on the best performing classifier and thus you find recommendations that will result in a change, but are not optimized to find the BEST END RESULT (e.g., maximum reduction in \# of defects, maximum reduction in \% likelihood of defect proneness.}
		   If none found, then repeat for $lvl += 1$. Also,
		    return nil  if the new $lvl$ is above the root. 
		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Now find $\Delta = C_+ - C_-$  by reflecting
	 on the set difference between  conditions in the decision tree branch to $C_-$ and $C_+$. To find that delta,
	 for discrete attributes, the delta is the value from {\em desired};
	    for numerics  expressed as ranges, the delta is a random number selected from the low and high boundaries of the that range.\footnote{This could lead to conflicting recommendations in different runs of XTREE, right? Consider Figure 3. Suppose $C_+$ has cbo=(27.00,157.00):1.00. XTREE ascends one level and descends to the leaves of next subtree. XTREE suppose that $C_-$ is a leaft where cbo=(1.00,50:00):0.15 (instead of cam as in Figure 3). By selecting something random in the range, you could recommend either an increase or a decrease to CBO. I would think that this is an instance where XTREE should say 'I don't know what to do with CBO, but you should improve LCOM.' Alternately, if you took the median value (instead of random) and coompared, you could at least recommend a direction, i.e., ``the best benefits come from REDUCING lcom while maintaining a LOWER cbo''}

@@

{\bf RQ1: Effectiveness: } which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? 
To   answer to this question, we will assume that developers
refactor their code until the bad smell thresholds are not violated.
This refactoring will start with some {\em initial} code
base that is changed to a {\em new} code base. 
For example, if the bad smell is \mbox{{\em loc $>100$}} and a 
code module has 500 lines of code, we reason
optimistically that we can change that code metric
to 100.  
Using the secondary verification oracle,  we then predict the
number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
The best bad smell threshold method is the one that maximizes
\begin{equation}\label{eq:diff}
\mathit{improvement} = 100* \left(1 - \frac{ d_- }{ d_+}\right)
\end{equation}

@@

{\bf RQ4: Stability:} Across different projects, how variable are the changes recommended by XTREE?   To answer this
question, we conduct a large scale ``what if'' study that reports all the possible recommendations XTREE might make.
We then count how often attributes are {\em not} found in the recommendations arising from this ``what if'' study.

{\bf RQ5: Conjunctive Fallacy:} Is  it  always  useful  to  apply \eq{df}; i.e.   make  code  better  by  reducing  the  values  of multiple code attributes? To answer this question, we will look at the {\em direction of change} seen in the {\bf RQ4} study; i.e.
how often does XTREE recommend decreasing or increasing a static code attribute.

@@

\subsection{Experiment}
Describe what you actually did, including: 
\bi
\item what metrics you used to identify refactorings using the 4 methods. Also, what is your data here? Is it the rows and columns of CK/OO metrics for each file?
\item how you applied the recommended changes from the 4 methods to the data 
\item how you chose to handle the ``conjuctive fallacy' of non-CD, non-XTREE methods
\item What are you considering correct, i.e., if the change to the code metrics yielded a non-defective (i.e., \# defects = 0) file, then the refactoring is good. 
\item how you aggregated the results from your 40 runs for each method
\ei

\subsection{Statistics}\footnote{You need a section before this called "Experiment"}.

@@

\fig{counts} shows the frequency with which the methods
recommend changes to specific code metrics.
Note that XTREE proposes thresholds to
few code metrics compared to the other approaches.

@@

{\em  How effective is XTREE at offering   ``stopping points'' (i.e. clear guidance on what not to do)?}

@@

\subsection{RQ5: Conjunctive Fallacy}

@@

To explore this point further, we conducted the following ``what-if'' study\footnote{What is the advantage of this ``what-if'' approach over just looking at the recommendations from the 40 runs in your experiments? Why not both?}. Once XTREE builds its trees with its leaf clusters then:
\be
\item For all clusters $C_0$, $C_1$ where the percent of defects in $C_0$ is greater than $C_1$...
\item For all attribute measures that are have a statistically significantly different distribution  between $C_0$ and $C_1$...
\item Report the direction of the change.
\ee
Note that the changes found in this way are somewhat more general than the above results
since they were  limited
to comments on the test set given to the program. The above three points comments on the direction of {\em all possible changes}
that XTREE could ever report
